---
output:
  word_document: default
  html_document: default
---

***Project***
## The Analysis of the Cold_Storage_Temp_Data
## By Chinedu.H. Obetta of Great Learning Academy

*** Part One***
## Setting up the working directory and Upload data into R using CSV file

```{r}
library(readr)
Cold_Storage_Temp_Data<-read.csv("Cold_Storage_Temp_Data.csv", header = TRUE)
dim(Cold_Storage_Temp_Data)
attach(Cold_Storage_Temp_Data)
head(Cold_Storage_Temp_Data, 4)

```
##1.	Find mean cold storage temperature for Summer, Winter and Rainy Season
** The by function will be used to determine the average cold storage temperature for each of the seasons
```{r}
attach(Cold_Storage_Temp_Data)
summary(Temperature)
boxplot(Temperature, horizontal = TRUE, title = "Box Plot For Temperature")
hist(Temperature)
by(Temperature, INDICES = Season, FUN = mean)
```

##2 To determine the  overall mean and Standard Deviation for the full year

```{r}
Overall_mean <- mean(Temperature)
Overall_Std <- sd(Temperature)
Overall_Std   
Overall_mean
```

##3&4 The probability of temperature having fallen below 2 C and the probability of temperature having gone above 4 C?
```{r}
Prob_Less_Than_2c<-pnorm(2, mean = Overall_mean, sd=Overall_Std)
Prob_Greater_Than_4c<- 1-pnorm(4, mean = Overall_mean, sd=Overall_Std)
print(Prob_Less_Than_2c)
print(Prob_Greater_Than_4c)
```
##6.Perform a one-way ANOVA test to determine if there is a significant difference in Cold Storage temperature between rainy, summer and winter seasons and comment on the findings.
#Step1 

```{r}
summary(Temperature)
hist(Temperature)
boxplot(Temperature, horizontal = TRUE)
```

#Step2: Frequency counts and mean of the COld Storage Temperature at different season
```{r}
table(Season)
tapply(Temperature, Season, mean)
```

#Step 3: Box Plot analysis of season

```{r}
library(ggplot2)
ggplot(Cold_Storage_Temp_Data, aes(x = Season, y = Temperature, color=Season)) +
geom_boxplot()
```
#step 4-Test for Normality

```{r}
shapiro.test(Temperature)
```

#Step 5: Test of Homogeneity of Variance for ANOVA
```{r}

library(Rcmdr) # for Levene test for homegeneity of variance
leveneTest(Temperature~Season, Cold_Storage_Temp_Data)
```

***Part 2** 
```{r}
Cold_Storage_Mar2018<-read.csv("Cold_Storage_Mar2018.csv")
head(Cold_Storage_Mar2018, 20)
```
## The summary of the data is shown below
```{r}
summary(Cold_Storage_Mar2018)
hist(Cold_Storage_Mar2018$Temperature)
boxplot(Cold_Storage_Mar2018$Temperature)
```

### 2.2 Question/State the Hypothesis, perform hypothesis test and determine p-value. T.test will be applied since population mean and sd are unknown

```{r}
t.test(Cold_Storage_Mar2018$Temperature, alternative = "greater", mu=3.9)

```
 ***END***
